Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-03 Scripts/Initial_Analysis.Rmd
Ezstimat change in results

  # Reads taxon data
  proportion_data <- fread(paste(result_path,"Proportion/","proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/.))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Propotion",sep=""))

@@

# Run results
Proportion_Results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid =ifelse(per_mid >= 25, 25,
                           ifelse(per_mid <= -25,-25,per_mid)
                           )
         )

@@

@@

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

gc()# clean ram
x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,25),
    breaks = seq(0,25,5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connectionsc.png",
         width = 10,
         height = 6,
         units = "in"
  )

>>>>

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion/"),"proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/historical))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Proportion",sep=""))

@@

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           )
         )

@@

# The path
path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")

@@

eez_centroid <- my_path("D",extra_path = "Spatial",name = "eez_centroids.csv",read = T)

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

gc()# clean ram

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_mid)),
    breaks = seq(0,max(Data$per_mid),5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connections_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )
